Embedded Scalars, Preferred Readings \& Prosody: {A}n Experimental Revisit

### 2015-11-01 text/paper/reviews_2/response_letter.md

# Response to editor and reviewer comments

First of all, we would like to thank the editor and the reviewers for their comments and suggestions and for carefully reading our manuscript. We addressed each of the points raised to the best of our abilities and think that the reviews substantially improved this work.

@@

The main changes from the previous version are:

1. careful reformulation of conclusions to be drawn from our data in line with reviewer 2's suggestions;

2. shortening of section 3 to remove unnecessary detail in predictions of "core theories";

3. addition of a few elements of emphasis in introduction, Section 4 and reflection section 6, in response to reviewer 2's comments showing that the previous version may not have made the motivation of our design sufficiently clear.

In the following we will give detailed responses to the comments.

@@

## Editor comments

>I would like to ask two things of you: 
>
>(1) have a good think about the balanced conclusion you draw (the data are hard for both sides of the theoretical divide --- reviewer 2: the data clearly favours grammaticalism) and address the reviewer's worry as good as you can (s/he can't be the only one interpreting your paper like that);

We agree that our previous version has not been ideally clear on this. It is not our intention to polarize by misleading rhetorics. We have tried to clarify in the current version what our main conclusions from our data are, namely:

a. we stress (even more than before) that grammaticalism qua "core theory" is compatible with our data, while traditionalism is not;

b. we further specify why we believe that grammaticalism qua "core theory" is *trivially* compatible with our data, because it would not be inconsistent with any possible outcome of our experiment;

c. the only auxiliary assumption for grammaticalism that is directly applicable to our experiment (selecting reading preferences in terms of logical strength alone) is not compatible with our data.

@@

>(2) rethink the value of the fine-grained description of the landscape of theoretical options (section 3.1/3.2).

Although we had thought that it would be good for the readers to see the full space of possible predictions about preference patterns that relevant "core theories" + "auxiliary hypotheses" give, we agree that it is not strictly necessary to introduce all of these fine-grained distinctions. We have therefore removed those chunks of Section 3 which are not strictly relevant for our overall discussions (including Table 2, which summarized the predictions). Some particular "auxiliary assumptions" are taken up in the discussion section 6, but only those that are relevant for the overall discussion, like Magri's appeal to obligatory exhaustification, which is an example for how grammaticalism could predict our data.

@@

## Reviewer 1

Reviewer 1 had only minor remarks, which we will address below.

@@

>It would help, in describing Figure 3, to mention that the sentences about them referred to letters and circles.

This was added to the text.

> Page 20, the Clifton et al. 2002 reference isn't really very relevant to the point being made. If the authors want to cite counterevidence, they would do better with Gilboy, E., Sopena, J., Clifton, C. Jr., & Frazier, L. (1995). Argument structure and association preferences in Spanish and English Compound NPs. Cognition, 54(131-167). But it's not necessary. The citation of Konieczny and  Hemforth says what needs to be said.

Good point. We simply removed the reference to Clifton et al. 2002. Citing counterevidence here is not very important, so we leave it at that.

@@

> Page 41, bottom, the references to Figure 16c doesn't seem to be correct.

Corrected!

## Reviewer 2

We tried our very best to address all of the issues raised by reviewer 2, and
paid particular attention to those issues flagged as most important by the
reviewer herself/himself or the editor.

@@

[In the following, we reproduce the full review and use boldface to indicate the aspects that subsequent comments target.]

>The authors have done a good job responding to the first round of feedback. As in the previous round of review, I believe the paper makes a valuable contribution to the literature on scalar strengthening, and that the paper should be published. However, I continue to believe there is room for improvement. Specifically, **I believe the paper can be streamlined by taking fuller advantage of previous results**, which I hope will also clarify the contributions that the paper makes. 
>
>My most important comment, which I'll try to spell out in Section 1 below, is that the question-answer structure of the paper does not come across as cleanly as it should. **To my mind, the paper aims to answer two questions: (i) Are embedded strengthenings licensed only under marked prosody, i.e., is the Prosodic Marking Hypothesis true? (ii) Are there preferences for the different readings predicted by theories of strengthening? If so, what are they, and how are they determined?** 
>
>I believe the paper answers (i) quite nicely, but it burdens the reader with too much irrelevant information in setting up and addressing the question (much of section 3 of the paper up to but not including section 3.3 on the Prosodic Marking Hypothesis). Concerning question (ii), the paper leaves it unresolved, which would be fine had the authors not mischaracterized the question by invoking the Strongest Meaning Hypothesis in the way that they did (as I hope to clarify below). If these issues could be resolved in a revised version, I would have no serious objection to publication.

We are sorry that we didn't specify these points clearly enough in our previous manuscript. We feel that this description of what the paper is about is unfortunately not entirely as we intended. This could lead to certain misunderstandings, so we clarify our position in the present manuscript. We have also added to the text (introduction, especially the relevant Section 4.4, section 6) to strengthen our view of and the motivation for out study.

One of our main goals in this paper is, indeed, to address the effects of prosody, but with a particular motivation, namely to rule out effects of "silent prosody" as confounds in the interpretation of earlier data. This is important because all previous experimental results that depend on visual presentation of sentences could, in principle, be subject to doubt if we hypothesize (like many do) that prosody plays a role in this domain. This also includes the results of Chemla & Spector. This is why we want to be more careful in this paper and not take for granted the conclusions of Chemla & Spector.

Our reluctance to accept Chemla & Spector's conclusions also comes from the recent critique of, in particular, Geurts & van Tiel, who argue that Chemla & Spector's results could be influenced unduly by pictorial effects. This is the main motivation for our incremental verification task, as argued in Section 4.4 and followed up in the reflection section 6.

@@

<!---Unfortunately, we do not understand in what sense the paper leaves question (ii) unresolved, according to the reviewer. To be clear on this, we wanted to get experimental evidence for preferences among putative readings, and we did. We also discuss whether these are predicted by the competing theories. We have adjusted the formulation of these conclusions according to the reviewer's well-taken suggestions in the new version (see below). We never meant to address the question how preferences are determined (and are not clear on what this should mean).-->

>Section 1: The question-answer structure of the paper
>
>It will help me to discuss the paper's contributions by taking Chemla & Spector (2011, hf. CS) as relevant background, as they also aimed to detect embedded readings in AS and ES sentences and found results that are sometimes supported but sometimes challenged by the present authors. I focus here on ES sentences, in part because AS sentences are not ideal for teasing apart "grammaticalism" from "unrestricted traditionalism", for reasons discussed in CS and elsewhere. My aim here is to identify some of the important empirical results from the current paper, and to relate them to questions (i) and (ii) above:
>
>Empirical Result (1): Like CS, but using a different method, the present authors find that embedded strengthenings are available.
>
>Consequences of (1): This result supports two of CS's claims. First, it provides further evidence for embedded strengthening (and hence, on the face of it, against Traditionalism -- pending further clarification of "typicality"), though of course it leaves open the question in (i) above. Second, ** (1) provides further support for CS's claim that the Strongest Meaning Hypothesis is probably *not* the right disambiguation principle (see note 6 of CS, and CS's section 5.5.2)**.

We are very grateful for drawing our attention to the fact that we should mention that Chemla & Spector have already discussed their data as countering the Strongest Meaning Hypothesis. We agree with this point but we believe that are providing further evidence that is relevant for this discussion, given the doubts that were brought forth against Chemla & Spector's design and interpretation and the additional doubts that arise from issues with "silent prosody".

@@

We have taken up the suggestion to shorten Section 3 in the way that the reviewer describes.

Considering the results and conclusions of Chemla & Spector, we are reluctant to accept these as given. Since our design was motivated by catering to the very problems raised for Chemla & Spector, we do believe that our data gives new and interesting information about preference of readings. This is also because, as we argue in Section 4.4, we explicitly compare data from embedded scalars with other ambiguous constructions in the same experiment (same method, same subject pool).

@@

We agree that our previous version did not make this clear enough. We reformulated relevant locations to make clear what our position is, namely (same as above):

a. we stress (even more than before) that grammaticalism qua "core theory" is compatible with our data, while traditionalism is not; 
b. still, we maintain that grammaticalism qua "core theory" is *trivially* compatible with our data, because it would not be inconsistent with any possible outcome of our experiment; 
c. the only auxiliary assumption for grammaticalism that is directly applicable to our experiment (selecting reading preferences in terms of logical strength alone) is not compatible with our data.

> Section 2: Minor comments/thoughts (feel free to ignore)
>
> A: "Exactly one" as monotonic: **The authors suggest, based on the "true" responses at Step 2, that some of their participants might have re-interpreted "exactly one" as "at least one." I'm wondering if there is a less radical way to make sense of their participants' behaviour: for what it's worth, my intuition is that there might be domain-restriction effects here.** There is exactly one uncovered bell at Step 2; thus, the sentence is literally true under a reading in which the domain of the quantifier is restricted to this one individual. I'm not exactly sure how to dissociate this suggestion from the authors', and I of course wouldn't insist that the authors do this. I raise the idea here simply for their consideration. With this in mind, in future work perhaps the authors might consider examining what would happen if Step 1 were followed instead by what is currently Step 3. The domain-restriction proposal would predict less "true" responses here because now there are two bells that are salient in the domain, but an "at least one" reading would still easily permit a "true" response here. (Note that getting rid of the current Step 2 is largely harmless, since global readings were basically absent in this paradigm.)

This is a good and interesting suggestion. But we see potential problems with this idea, but feel that discussing this would lead us too far away from our main concerns.

@@

> B: The Strongest Meaning Hypothesis, Again: **As I noted earlier, it does not seem appropriate to assume the SMH for this paradigm in light of CS's results and discussion.** However, I should like to add that one has to be careful about what the SMH actually states when we consider exhaustification, and here perhaps CS themselves could have been more careful. When we compare the strength of various sentences that differ in the placement of EXH, we have to be careful about what the alternatives to EXH are. So far as I can tell, the SMH may well still be in the running as a disambiguation criterion, if only we could be sure what the alternatives are in any given experimental setup. Since we don't know this, we can't really be sure whether the SMH has been properly tested.

As mentioned above, we are grateful for reminding us to take into consideration Chemla & Spector's discussion of the SMH in this case. Their footnote 6 makes a similar point to the reviewer's. We acknowledge that Chemla & Spector believe that logical strength may still play a role despite their findings and that this may also extend to our findings in the reflection section 6. But we have no strong vision of how this idea could be realized and so must leave it for future work without too much speculation from our side here.

> Having said this, **it's still not clear to me that there is any motivation to appeal to the SMH the way the authors do.** Putting aside the issues raised earlier, it is important to note that **the works that the authors cite were all very careful to limit the immediate applicability of the SMH to either reciprocals (Dalrymple et al.) or to plural predication more generally (Winter). One is of course welcome to try extending its applicability, but my reading of the literature is that the SMH was not intended as a general disambiguation principle** (lest it run into well-known issues in other areas, e.g., preferences in scope-ambiguities).

It seems that we have reached rock bottom here, where the reviewer's view differs irresolvably from ours. Chierchia, Fox and Spector (2012, "The Grammatical View of Scalar Implicatures and the Relationship between Semantics and Pragmatics") suggest to use the SMH for disambiguating parses. We therefore think that it is appropriate to pay attention to the SMH, especially, as we stress, our emphasis on it is because it is the only fully spelled out proposal for enriching grammaticalism that applies to our abstract experimental setting. (This also relates to the following point about *ex ante* predictions; we take full blame for misunderstandings due to lack of careful enough explanation of what we mean by this term.)

@@

> C: "Ex ante" predictions: **The authors in many places write that certain proposals are not formulated as "ex ante" predictions. But the predictions of all the theories the authors discuss are all fully predictive: given a sentence and a context, just about every theory of strengthening I know clearly predicts how a scalar sentence will be interpreted.** Of course, in experimental settings many relevant features of the context are left open, and hence participants have to guess what context they're in (see e.g., Crain & Steedman, 1985). This is certainly the case for the author's experiment, in which many of the contextual features that are important for strengthening are unspecified (e.g., relevance, assumptions about the speaker's mental state, etc). But this is a general feature of psycholinguistic studies, is it not? If you leave open crucial contextual features, participants have to guess those values. Does this make the theories any less predictive? Is the difficulty in pinning down a context a difficulty for the theory or for the experimenter?

We are grateful for this comment, because it shows that we have been insufficiently clear on our intended meaning of *ex ante* predictions. We have clarified this more in the text (Section 3). We are interested in *ex ante* predictions *for our experiment*, not general predictions *given a set of contextual parameters*. We fully agree that abstract experimental setting underspecify relevant contextual parameters. We also therefore agree that our data does not speak against grammaticalism as a "core theory". We hope to have amended all relevant formulations in line with the reviewer's comments, so as not to give rise to misleading readings of our intended interpretation of our results.

### 2015-11-01 text/paper/revision_02/paper.tex
rev 2 final edits

\begin{abstract}
  The scalar item \emph{some} is widely assumed to receive a meaning
  enrichment to \emph{some but not all} if it occurs in matrix
  position. The question under which circumstances this enrichment can
  occur in certain embedded positions plays an important role in
  deciding how to delineate semantics and pragmatics. % Some claim
  % that it requires marked intonation for the relevant pragmatic
  % enrichment to occur in embedded position; others allow for it more
  % freely.
  We present new experimental data that bear on this theoretical issue. In distinction to
  previous experimental approaches, we presented sentence material auditorily in order to
  explicitly control prosodic markedness of the scalar item. Moreover, our experiment sheds
  light on the relative preferences or salience of candidate readings. The presented data turn
  out to be unexpected under a traditional Gricean view, but also challenge the idea that of
  disambiguation by logical strength in grammaticalist approaches.
\end{abstract}

@@

To deal with the problem of ``silent intonation,'' this paper presents results from an
experimental study which presented sentence materials auditorily and explicitly manipulated
contrastive stress on embedded scalar items. To address worries about pictorial ``typicality
effects,'' we employed an \emph{incremental verification task} in which parts of a
to-be-evaluated picture were hidden and only revealed piece-wise at the participants’ request
until they felt able to give a binary truth-value judgement \citep[see][]{Conroy2008}. In order
to obtain information about salience of readings, we use both a classical regression analysis
and a Bayesian statistical model to analyze the data from this novel task, and validate this
method by including control conditions testing ambiguous sentences with a well-known preference
on available readings. % We argue that this method provides categorical behavioral data that is
% both indicative of the reading preferences among participants and largely independent of
% potential pictorial confounds, such as the mentioned typicality effects.

@@

Traditionalism's predictions about preferences among available readings depend whether the
speaker is (most likely) knowledgeable in the relevant sense. We predict a strong non-epistemic
implicature that a given alternative is false if the speaker is assumed to be competent;
otherwise the preferred reading would be a literal reading or a weak epistemic implicature
(that the speaker does not know whether the alternative is true). In the context of a given
abstract experiment that does not manipulate speaker expertise (like ours), it is then
\emph{prima facie} compatible with a traditionalist position to expect literal or implicature
readings to be more prominent.

@@

It is a topic of active current debate as to how a grammaticalist
approach should be supplemented with a general and well-motivated
\emph{disambiguation criterion} so as to rule out unattested readings
obtainable by embedded exhaustification and to make concrete
predictions about preferences over readings made
available. % Grammaticalists therefore
% acknowledge that \emph{some} disambiguation principle must be
% specified, for otherwise grammaticalism would hardly make any
% commitment and would overpredict readings in cases where they are
% unattested, i.e., when scalar items appear in downward-entailing
% contexts \citep[c.f.][for explicit
% discussion]{FoxSpector:Economy-and-Emb}.
Several approaches have been suggested in the literature
\citep[c.f.][]{ChemlaSingh2014:Remarks-on-the-}. We focus here on the one that is least
controversially applicable to our experimental case, and that has theoretical significance
beyond the debate about embedded implicatures: disambiguation by comparison of logical
strengths, as suggested by the \emph{strongest meaning hypothesis} of
\citet{DalrympleKanazawa1998:Reciprocal-Expr}.\footnote{We will come back to other
  implementations of grammaticalism in Section~\ref{sec:critical-reflection}.}

% To start with,
% \citet{Magri2009:A-Theory-of-Ind,Magri2011:Another-Argumen} opts for
% obligatory presence of $\exh(\cdot)$ with variability in the set of
% alternatives to feed into each $\exh(\cdot)$. Under this approach,
% alternatives may be pruned entirely, so that all occurrences of
% $\exh(\cdot)$ become vacuous, resulting in a literal reading. Whether
% alternatives apply or not is a matter of their relevance. It is not
% clear what his approach predicts \emph{ex ante} about the relative
% salience of candidate readings in a neutral experiment that does not
% explicitly provide information about which alternatives are relevant
% (for whatever purpose). However, we will show in
% Section~\ref{sec:critical-reflection} that Magri's approach can be
% brought to accommodate the data very well after the fact.

% Other proponents of grammaticalism assume that insertion of $\exh(\cdot)$ is
% optional. Under one proposal for disambiguation, readings are the more
% preferred the better they answer the contextually given question under
% discussion (QUD)
% \citep[e.g.][]{Fox2007:Free-Choice-and,GualminiHulsey2008:The-Question-An}. This
% is a plausible suggestion, but does not give clear predictions for a
% case like our experiment without fixed QUD. Subjects could in
% principle accommodate any QUD, so that this approach would not
% restrict the space of reading preferences either.

Supplementing grammaticalism with a strength-based selection criterion has been suggested, in
one form or another, in many contributions to this paradigm
\citep[e.g.][]{FoxSpector:Economy-and-Emb,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and,Spector2014:Global-Positive}. At
the same time, the strongest meaning hypothesis has been frequently called upon for
disambiguation purposes in other domains as well, including reciprocals
\citep{DalrympleKanazawa1998:Reciprocal-Expr}, plural predication
\citep{Winter2001:Plural-Predicat} or vagueness \citep{CobrerosEgre2012:Tolerant-Classi}. The
main reason, however, why we focus on strength based disambiguation is because it is, as far as
we can say, the only disambiguation mechanism for grammaticalism suggested in the literature
that gives predictions about potential outcomes of our experiment \emph{ex ante}, i.e., before
having seen any data of that experiment.\footnote{See also
  \citet{ChemlaSpector2010:Experimental-Ev} for insightful discussion of strength-based
  disambiguation in the light of their experimental results.}

Most straightforwardly, disambiguation by logical strength predicts that preferences for
readings would just mirro mirror the entailment relations in (\ref{bsp:Entailments-AS}) and
(\ref{bsp:Entailments-GE}): for \as-sentences, weak grammaticalism predicts that local readings
are preferred over global readings which in turn are preferred over literal readings; for
\es-sentences weak grammaticalism predicts that global readings are most preferred, while
literal and local readings are not ranked with respect to
preference.\footnote{\citet{ChierchiaFox2008:The-Grammatical} consider another, more elaborate
  variant of disambiguation based on strongest meanings, but it is not necessary for purposes
  to discuss these details here.}

@@

\noindent The \emph{prosodic markedness hypothesis}, as we will call it here, is then an
addition to the traditionalist's explanatory repertoire. Under this extra assumption, local
readings are a marked phenomenon, and not the product of the same process as run-of-the-mill
scalar implicatures. If supplemented with the prosodic markedness hypothesis, traditionalists
would therefore predict that local readings are available for \es-sentences, but only if
prosodically marked by contrastive stress.

@@

\paragraph{General motivation.} To deal with desiderata (i) and (ii), we used an
\emph{incremental verification task} (\acro{ivt}), which is a modified version of picture
verification \citep[see][]{Conroy2008}. The general idea is that subjects are requested to
judge sentence material with respect to pictures that do not necessarily contain all the
information relevant for judging a certain reading true or false. In that case, participants
can demand that more information be revealed. Participants are instructed to make a truth-value
judgment as soon as they are able to. When they do, the trial ends. Motivated by desideratum
(iii), we include ``preference-related control'' conditions. Sentence material was presented
auditorily and we manipulated prosodic realization to cater for desideratum (iv).

@@

\begin{exe}
\ex \gll Der Brief ist mit Kreisen und Vierecken mit Sonnen
  verbunden. \label{bsp:target-related}\\
The letter is with circles and squares with suns connected.\\
The letter is connected with circles and squares with suns.
\begin{xlist}
  \ex \label{bsp:target-related-LC} The letter is connected with squares containing suns, and it is
    also connected with circles. \hfill{(\lc)}
  \ex \label{bsp:target-related-EC} The letter is connected with circles and squares, both of which
    are containing suns.  \hfill{(\ec)} 
\end{xlist}
\end{exe}
In attachment ambiguities involving post-nominal modification, an
adjunct like a relative clause or a prepositional phrase (\acro{pp})
can be attached to one of two preceding hosts.  For instance, in
(\ref{bsp:target-related}), the \acro{pp} \emph{with suns} can be
attached to the preceding noun \emph{squares}, resulting in the
so-called \emph{late-closure} (\lc) reading
((\ref{bsp:target-related-LC}). Alternatively, the \acro{pp} can be
attached to the whole conjunctive \acro{np} \emph{circles and
  squares}, corresponding to the \emph{early-closure} (\ec) reading
(\ref{bsp:target-related-EC}).  \lc-readings have been generally
observed to be preferred over \ec-readings (e.g., \cite{Fodor98} for
an overview of different languages, but see also
\cite{CliftonCarlsonFrazier2002} for counterevidence). Crucially, an
\lc-preference for \acro{pp}-attachment structures has also been
attested for German \citep[][]{KoniecznyHemforth2000}.

@@

We fitted generalized linear models to the count data in
Table~\ref{tab:count_data_CC}, using factors \textsc{Condition} with
levels \as and \es, \textsc{Accent} with levels \emph{neutral} and
\emph{accented}, and \textsc{Trial} with levels 1 through 3 (coding
whether it was the first, second or third time that a participant saw
a critical condition during the experiment) to predict the dependent
factor \textsc{Reading} with levels \emph{literal}, \emph{local}, and
\emph{other}. The latter lumps \emph{global} and \emph{error}
responses together, because otherwise we would not have enough cell
counts to apply log-linear regression. We determined the ``best''
model of the data by a gradient search over hierarchical models in
terms of AICs, starting from the saturated model. The best model takes
main factors \textsc{Reading} and \textsc{Condition} into account, as
well as the interaction term \textsc{Reading:Condition} ($\chi^2 =
17.19$, $df=42$, $p = 0.99$, $AIC = 158.01$ (compared to $AIC=208.25$
of the saturated model)). Crucially, factors \textsc{Trial} and
\textsc{Accent} were dropped in the best model. This suggests that
response patterns only depend on the type of the sentence, but that
there were no learning or fatigation effects and that accentuation did
not influence answer patterns significantly (at this level of
abstraction).

\begin{table}
  \centering
  \begin{tabular}{lllll}
    coefficient & estimate & std.~error & $z$-value & $\Pr(>|z|)$ \\
    \midrule
    \textsc{Intercept} & 0.916  &  0.258 &  3.49  & < 0.001 \\
    \textsc{Reading}.\emph{literal} & 2.600 &   0.268 & 9.716 & < 0.001 \\
    \textsc{Reading}.\emph{local} & -0.310  &  0.397 & -0.781 &
    0.435 \\
    \textsc{Condition}.\es & 1.030 &  0.301 & 3.423 &  < 0.001 \\
    \textsc{Reading}.\emph{literal}:\textsc{Condition}.\es & -1.288 &
    0.319 & -4.036 &  < 0.001 \\
    \textsc{Reading}.\emph{local}:\textsc{Condition}.\es & -0.026 &
    0.463 &  -0.0579 &  0.955
  \end{tabular}
  \caption{Coefficients of the ``best'' log-linear model for the count
    data in Table~\ref{tab:count_data_CC}.}
  \label{tab:Coefficients-CC}
\end{table}

@@

As for the critical conditions, we computed logistic regression models
including factors \textsc{Reading} with levels \lc, \ec and
\emph{error}, \textsc{Accent} with levels \emph{neutral},
\emph{\lc-cue} and \emph{\ec-cue}, \textsc{Trial} with levels 1 to
3, and \textsc{Condition} with levels \lc and \ec for the picture
sequences. Starting search from the saturated model along a gradient
of decreasing AICs, we find that the ``best'' model relies on main
effects of \textsc{Reading}, \textsc{Accent} and \textsc{Condition}
and two two-way interactions \textsc{Reading:Condition} and
\textsc{Reading:Accent} ($\chi^2=18.34$, $df=42$, $p=0.99$,
$AIC=256.63$ (compared to $AIC=322.3$ of the saturated model)). Factor
\textsc{Trial} was dropped from the best model, suggesting that
answer patterns are stable over the duration of the experiment. Unlike
for the critical conditions, factor \textsc{Accent} is retained, and
it interacts with \textsc{Reading}, suggesting that prosodic cues
significantly influenced the dominant reading.

>>>>

\begin{abstract}
  The scalar item \emph{some} is widely assumed to receive a meaning
  enrichment to \emph{some but not all} if it occurs in matrix
  position. The question under which circumstances this enrichment can
  occur in certain embedded positions plays an important role in
  deciding how to delineate semantics and pragmatics. % Some claim
  % that it requires marked intonation for the relevant pragmatic
  % enrichment to occur in embedded position; others allow for it more
  % freely.
  We present new experimental data that bear on this theoretical issue. In distinction to
  previous experimental approaches, we presented sentence material auditorily in order to
  explicitly control prosodic markedness of the scalar item. Moreover, our experiment sheds
  light on the relative preferences or salience of candidate readings. The presented data turn
  out to be unexpected under a traditional Gricean view, but also challenge the idea of
  disambiguation by logical strength in grammaticalist approaches.
\end{abstract}

@@

To deal with these methodological concerns, this paper presents results from an
\emph{incremental verification task}. In order to address the problem of silent prosody, we
presented sentence materials auditorily and explicitly manipulated contrastive stress on
embedded scalar items. Moreover, to address worries about pictorial “typicality effects,” parts
of a to-be-evaluated picture were hidden and only revealed piece-wise at the participants’
request until they felt able to give a binary truth-value judgement
\citep[see][]{Conroy2008}. In order to obtain information about salience of readings, we use
both a classical regression analysis and a Bayesian statistical model to analyze the data from
this novel task, and validate this method by including control conditions testing ambiguous
sentences with a well-known preference on available readings.

@@

Traditionalism’s predictions about preferences among available readings depend on the
reliability of contextual information, such as speaker knowledgeability. Specifically,
considering a speaker knowledgeable results in a strong non-epistemic implicature that a given
alternative is false. By contrast, considering a speaker as ignorant results in a literal
reading or a weak epistemic implicature (that the speaker does not know whether the alternative
is true). In the context of a given abstract experiment that does not manipulate speaker
expertise (like ours), it is then \emph{prima facie} compatible with a traditionalist position
to expect literal or implicature readings to be more prominent \citep[see][for experimental
data on this]{GoodmanStuhlmuller2013:Knowledge-and-I}.

@@

It is a topic of active current debate as to how a grammaticalist
approach should be supplemented with a general and well-motivated
\emph{disambiguation criterion} so as to rule out unattested readings
obtainable by embedded exhaustification and to make concrete
predictions about preferences over readings made
available. % Grammaticalists therefore
% acknowledge that \emph{some} disambiguation principle must be
% specified, for otherwise grammaticalism would hardly make any
% commitment and would overpredict readings in cases where they are
% unattested, i.e., when scalar items appear in downward-entailing
% contexts \citep[c.f.][for explicit
% discussion]{FoxSpector:Economy-and-Emb}.
Several approaches have been suggested in the literature
\citep[c.f.][]{Fox2007:Free-Choice-and,Magri2009:A-Theory-of-Ind,ChemlaSingh2014:Remarks-on-the-}.

To our knowledge, only one of these proposed disambiguation mechanisms is principally able to
give predictions about potential outcomes of our experiment \emph{ex ante}, i.e., before having
seen any data of that experiment. The \emph{strongest meaning hypothesis} of
\citet{DalrympleKanazawa1998:Reciprocal-Expr} involves a disambiguation mechanism by comparison
of logical strengths. Supplementing grammaticalism with a strength-based selection criterion
has been suggested, in one form or another, in many contributions to this paradigm
\citep[e.g.][]{FoxSpector:Economy-and-Emb,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and,Spector2014:Global-Positive}. At
the same time, the strongest meaning hypothesis has theoretical significance beyond the debate
about embedded implicatures and has been frequently called upon for disambiguation purposes in
other domains, including reciprocals \citep{DalrympleKanazawa1998:Reciprocal-Expr}, plural
predication \citep{Winter2001:Plural-Predicat} or vagueness
\citep{CobrerosEgre2012:Tolerant-Classi}.

Most straightforwardly, disambiguation by logical strength predicts that preferences for
readings would just mirror the entailment relations in (\ref{bsp:Entailments-AS}) and
(\ref{bsp:Entailments-GE}): for \as-sentences, weak grammaticalism predicts that local readings
are preferred over global readings which in turn are preferred over literal readings; for
\es-sentences weak grammaticalism predicts that global readings are most preferred, while
literal and local readings are not ranked with respect to
preference.\footnote{\citet{ChierchiaFox2008:The-Grammatical} consider another, more elaborate
  variant of disambiguation based on strongest meanings, but it is not necessary for purposes
  to discuss these details here.}

@@

\noindent The \emph{prosodic markedness hypothesis}, as we will call it here, is then an
addition to the traditionalist's explanatory repertoire. Under this extra assumption, local
readings are a marked phenomenon, and not the product of the same process as run-of-the-mill
scalar implicatures. If supplemented with the prosodic markedness hypothesis, traditionalists
would therefore predict that local readings are available forK \es-sentences, but only if
prosodically marked by contrastive stress.

@@

\paragraph{General motivation.} To deal with desiderata (i) and (ii), we used an
\emph{incremental verification task} (\acro{ivt}), which is a modified version of picture
verification \citep[see][]{Conroy2008}. The general idea is that subjects are requested to
judge sentence material with respect to pictures that do not necessarily contain all the
information relevant for judging a certain reading true or false. In that case, participants
could demand that more information be revealed. Participants were instructed to make a
truth-value judgment as soon as they were able to do so. When they did, the trial
ended. Motivated by desideratum (iii), we included ``preference-related control''
conditions. The sentence materials were presented auditorily and we manipulated the prosodic
realization to cater for desideratum (iv).

@@

\begin{exe}
\ex \gll Der Brief ist mit Kreisen und Vierecken mit Sonnen
  verbunden. \label{bsp:target-related}\\
The letter is with circles and squares with suns connected.\\
The letter is connected with circles and squares with suns.
\begin{xlist}
  \ex \label{bsp:target-related-LC} The letter is connected with squares containing suns, and it is
    also connected with circles. \hfill{(\lc)}
  \ex \label{bsp:target-related-EC} The letter is connected with circles and squares, both of which
    are containing suns.  \hfill{(\ec)} 
\end{xlist}
\end{exe}
In attachment ambiguities involving post-nominal modification, an
adjunct like a relative clause or a prepositional phrase (\acro{pp})
can be attached to one of two preceding hosts.  For instance, in
(\ref{bsp:target-related}), the \acro{pp} \emph{with suns} can be
attached to the preceding noun \emph{squares}, resulting in the
so-called \emph{late-closure} (\lc) reading
((\ref{bsp:target-related-LC}). Alternatively, the \acro{pp} can be
attached to the whole conjunctive \acro{np} \emph{circles and
  squares}, corresponding to the \emph{early-closure} (\ec) reading
(\ref{bsp:target-related-EC}).  \lc-readings have been generally
observed to be preferred over \ec-readings (e.g., \cite{Fodor98} for
an overview of different languages). Crucially, an
\lc-preference for \acro{pp}-attachment structures has also been
attested for German \citep[][]{KoniecznyHemforth2000}.

@@

We fitted generalized linear models to the count data in
Table~\ref{tab:count_data_CC}, using factors \textsc{SentenceType} with
levels \as and \es, \textsc{Accent} with levels \emph{neutral} and
\emph{accented}, and \textsc{Trial} with levels 1 through 3 (coding
whether it was the first, second or third time that a participant saw
a critical condition during the experiment) to predict the dependent
factor \textsc{Reading} with levels \emph{literal}, \emph{local}, and
\emph{other}. The latter lumps \emph{global} and \emph{error}
responses together, because otherwise we would not have enough cell
counts to apply log-linear regression. We determined the ``best''
model of the data by a gradient search over hierarchical models in
terms of AICs, starting from the saturated model. The best model takes
main factors \textsc{Reading} and \textsc{SentenceType} into account, as
well as the interaction term \textsc{Reading:Condition} ($\chi^2 =
17.19$, $df=42$, $p = 0.99$, $AIC = 158.01$ (compared to $AIC=208.25$
of the saturated model)). Crucially, factors \textsc{Trial} and
\textsc{Accent} were dropped in the best model. This suggests that
response patterns only depend on the type of the sentence, but that
there were no learning or fatigation effects and that accentuation did
not influence answer patterns significantly (at this level of
abstraction).

\begin{table}
  \centering
  \begin{tabular}{lllll}
    coefficient & estimate & std.~error & $z$-value & $\Pr(>|z|)$ \\
    \midrule
    \textsc{Intercept} & 0.916  &  0.258 &  3.49  & < 0.001 \\
    \textsc{Reading}.\emph{literal} & 2.600 &   0.268 & 9.716 & < 0.001 \\
    \textsc{Reading}.\emph{local} & -0.310  &  0.397 & -0.781 &
    0.435 \\
    \textsc{SentenceType}.\es & 1.030 &  0.301 & 3.423 &  < 0.001 \\
    \textsc{Reading}.\emph{literal}:\textsc{SentenceType}.\es & -1.288 &
    0.319 & -4.036 &  < 0.001 \\
    \textsc{Reading}.\emph{local}:\textsc{SentenceType}.\es & -0.026 &
    0.463 &  -0.0579 &  0.955
  \end{tabular}
  \caption{Coefficients of the ``best'' log-linear model for the count
    data in Table~\ref{tab:count_data_CC}.}
  \label{tab:Coefficients-CC}
\end{table}

@@

As for the critical conditions, we computed logistic regression models
including factors \textsc{Reading} with levels \lc, \ec and
\emph{error}, \textsc{Accent} with levels \emph{neutral},
\emph{\lc-cue} and \emph{\ec-cue}, \textsc{Trial} with levels 1 to
3, and \textsc{Picture} with levels \lc and \ec for the picture
sequences. Starting search from the saturated model along a gradient
of decreasing AICs, we find that the ``best'' model relies on main
effects of \textsc{Reading}, \textsc{Accent} and \textsc{Picture}
and two two-way interactions \textsc{Reading:Picture} and
\textsc{Reading:Accent} ($\chi^2=18.34$, $df=42$, $p=0.99$,
$AIC=256.63$ (compared to $AIC=322.3$ of the saturated model)). Factor
\textsc{Trial} was dropped from the best model, suggesting that
answer patterns are stable over the duration of the experiment. Unlike
for the critical conditions, factor \textsc{Accent} is retained, and
it interacts with \textsc{Reading}, suggesting that prosodic cues
significantly influenced the dominant reading.
